Comparison of simulation to theory

### 2016-02-25 sims/compare-to-theory.Rmd

We'll do this against $x$ at a few values of $r$ because that's what we have.
```{r theory_haps, cache=TRUE}
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=41)
# hap.soln <- forwards_backwards_haplotypes(s=theory.params$s, times=tt, xgrid=xgrid, rgrid=rgrid,
#                            sigma=theory.params$sigma, 
#                            fwds.grid=fgrid, fwds.soln=fwds.soln )
```

>>>>

We'll do this against $x$ at a few values of $r$ because that's what we have.
```{r theory_haps, cache=TRUE}
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=41)
hap.soln <- forwards_backwards_haplotypes(s=theory.params$s, times=tt, xgrid=xgrid, rgrid=rgrid,
                           sigma=theory.params$sigma, 
                           fwds.grid=fgrid, fwds.soln=fwds.soln )
```
